\cvsection{Experience}
\begin{cventries}
  \cventry
    {Basekernel Research}
    {Professor Douglas Thain}
    {Notre Dame, Indiana}
    {Jan. 2018 - Present}
    {
      \begin{cvitems}
        \item {{\bf https://github.com/dthain/basekernel} - Contributor for basekernel, an minimal kernel based on the idea of hierarchical containment.}
      \end{cvitems}
    }
  \cventry
    {Frontend Web Developer}
    {South Bend Code School}
    {South Bend, Indiana}
    {Aug. 2017 - Present}
    {
      \begin{cvitems}
        \item {Web Developer consulting with local companies through South Bend Code School.}
        \item {{\bf https://portal.atlas3d.xyz} - Main developer on Vue.js single page app which interfaces with GraphQL database.  Allows users to upload 3D models and optimize them for minimum build time, material consumption, or other factors.}
        \item {{\bf Notre Dame Benefits page} - Assistant developer on internal pug html static site.  Used to calculate benefits for prospective employees.}
      \end{cvitems}
    }
  \cventry
    {Donation Facilitator}
    {Notre Dame Alumni Center}
    {Notre Dame, Indiana}
    {Sep. 2016 - May. 2017}
    {
      \begin{cvitems}
        \item {Facilitated financial contributions to the University for various causes and campaigns.}
        \item {Exceeded the average amount of donations by more than 17\% in every report.}
      \end{cvitems}
    }
  \cventry
    {Data Analysis \& Visualization Intern}
    {Fermilab}
    {Batavia, Illinois}
    {Jun. 2015 - Jul. 2015}
    {
      \begin{cvitems}
        \item {Improved the data reduction pipeline for a new type
of telescope camera.}
        \item {Automated various data visualization techniques in Python.}
        \item {Collaborated with a team of about 20 on the camera’s data processing, error analysis modules, and documentation.}
      \end{cvitems}
    }
\end{cventries}
